### 2021-03-04 paper3/paper3.tex
Make it compile with the 3rd paper

%\icmltitle{Learning with Perfect Bags:\\
%Addressing Hidden Stratification with Zero Labelled Data}

@@

Specifically, our paper provides the following contributions:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item An example of systematic bias leading to one or more  subgroups having \emph{zero labelled data}.
    \item Applying clustering methods to the task of transforming an \emph{unlabelled dataset} into perfect bags.
    \item Theoretical and experimental justification that the disentangling model with \emph{the perfect bag as an inductive bias} provides a well-disentangled representation, where one component captures the subgrouping factors and another component is invariant to them.
    \item A new parametric approach to disentangling that combines elements from adversarial learning and set-classification to guide an encoder network towards the goal of producing encodings invariant to the source distribution and thereby the subgroup factors in which source distributions differ.
\end{enumerate}

@@

%\begin{wrapfigure}{!t}{0.6\textwidth}
\begin{figure*}[ht]
\centering
\begin{subfigure}[b]{0.74\textwidth}
    \centering
    %\includegraphics[width=0.9\textwidth]{figures/SSL-framework}
    % \includegraphics[width=\textwidth]{figures/SSL-framework-withPred.pdf}
    \includegraphics[width=\textwidth]{figures/zsf_diagram.pdf}
    \caption{%
    The main components involved in our proposed disentangling method, $f_y$ (debiaser) and $h$ (discriminator). The debiaser is trained to produce encodings, $z_y$ of the data that are invariant to the source dataset and thereby the subgroups identifying it. In order to determine whether a bag of encodings originates from the training set or the deployment set, the discriminator performs an attention-weighted aggregation over the bag dimension to model interdependencies between the samples. In the case of Coloured MNIST where {\color{purple}purple} fours constitute the missing subgroup, the discriminator can identify an encoding of a bag from the training set by the absence of such samples so long as colour information is detectable in $z_y$, serving as an error signal for the debiaser.
    }%
    \label{fig:architecture}
\end{subfigure}%
% \end{figure}
%\end{wrapfigure}
\hfill
% \begin{figure}
\begin{subfigure}[b]{0.24\textwidth}
    \centering
    % if you want to make changes to the diagram, it is located here:
    % https://drive.google.com/file/d/1M37m4rVj1EGrFJb9QzK32bs8swepiaZ1/view?usp=sharing
    \includegraphics[width=\textwidth]{figures/fdm.pdf}
    \caption{%
    Illustration of distribution matching.
    In this example, the training set is lacking {\color{purple}purple} 4's.
    By enforcing the subspace $z_y$ to have the same distribution for both the training and deployment set, the model is encouraged to learn a representation that is invariant to colour (or $s$ in general.)
    For this to work, it is crucial that the bags be approximately balanced (perfect bags).
    }%
    \label{fig:matching-diagram}
\end{subfigure}
\caption{%
Overview of the disentangling framework with a perfect (balanced) bag as an inductive bias.
}%
\label{fig:framework}
\end{figure*}

@@

\textbf{Zero-label stratification and algorithmic bias.}
Let $S$ denote a set of discrete-valued subgroup labels of the associated domains $\Scal$.
%
% $S$ can take the values taken by a single subclass label, or, $S = S_1 \times S_2 \times \ldots \times S_p$ with $S_1, \ldots, S_p$ be discrete-valued subclass labels more generally.
%
$X$, with the associated domain $\Xcal$, represents other attributes of the data. % that may or may not be influenced by subgroup labels $S$.
%
Let $\Ycal$ denote the space of class labels for a classification task; $\Ycal = \{0,1\}$ for binary classification or $\Ycal = \{1,2,\ldots,C_{\text{cls}}\}$ for multi-class classification.
%
For ease of exposition, we assume that we have multiple sources $\Omega$ of samples, one for each combination of class-label $y$ and subgroup-label $s$.
That is, we have:
\begin{align}
\Omega_{y=y',s=s'},\quad\quad\forall y'\in\mathcal{Y},\forall s'\in\mathcal{S},
\end{align}
where, for example, the source $\Omega_{y=0,s=0}$ supplies all data points with class label $y=0$ and subgroup label $s=0$. 
%
As in a standard supervised learning task, we have access to a labelled training set $\Dcal_{tr} =\{(x_i, s_i, y_i)\}$, that is used to learn a model $M:\Xcal \rightarrow \Ycal$. 
$\Dcal_{tr}$ is composed of several sources, but lacks samples from some of the sources:
\begin{align}
\exists y'\in \Ycal,\exists s'\in \Scal: \Dcal_{tr}\cap \Omega_{y=y',s=s'} = \varnothing.
\end{align}
For example, we might be missing samples from two sources: $\Omega_{y=0,s=0}$ and $\Omega_{y=1,s=0}$. 
%
In binary classification, this corresponds to no labelled data for the subgroup label $s=0$, a setting we refer to as \emph{missing subgroup} (MS).
%
Other times, we may observe a one-sided (negative) outcome for the subgroup label $s=0$
(\ie, we have $\Dcal_\mathit{tr} \cap\Omega_{y=1,s=0} = \varnothing$), giving rise to a setting we refer to as \emph{subgroup bias} (SB).

@@

%Semi-supervised learning \cite{ChaSchZie06} can alleviate the issue of unfairness to the \emph{invisibles} by mixing labeled with unlabeled data, which is usually much cheaper to obtain. 
%
We propose to alleviate the issue of bias against missing subgroups by mixing labelled data with unlabelled data that is usually much cheaper to obtain \cite{ChaSchZie06}. 
%
In this paper, we refer to this set of \emph{unlabelled} data as the
deployment set\footnote{In our experiments, we report accuracy and bias metrics on another independent test set instead of on the unlabelled data that is available at training time.} $\Dcal_{dep} =\{(x_i)\}$.
%_{i=1}^{N^c}
%
This 
%context 
deployment set has overlap with all sources:
\begin{align}
  \Dcal_{dep} \cap \Omega_{y=y',s=s'} \neq \varnothing\quad\quad\forall y'\in\Ycal,\forall s'\in\Scal~.
\end{align}
%The deployment set is much like the deployment set: 
Importantly, the deployment set has no information about class labels $y$ or the subgroup labels $s$.

@@

\textbf{Disentangled representation.}
Disentanglement-learning aims to find a factorised representation of a data point $x$ through mapping functions $f_i$ such that $f_i(x)=z_i$ where $z_1,z_2,\ldots,z_p$ are $p$ distinct (independent) factors of variations, which together form $x$.
%
We can formalise this intuitive definition using group and representation theories \cite{HigAmoPfaRacetal18}, or using structural causal models \cite{SutMilSchBau19}.
%
Specifically for this paper, we would like to split the data representation into two factors as $f_y(x)=z_y$ and $f_s(x)=z_s$ where $z_y$ contains factors that are relevant for $y$-prediction and $z_s$ contains factors related to the subgroup label $s$.
%
Since $s$ is correlated with the class label $y$, we need annotations of the undesired nuisance variable $s$ \cite{JaiRexAbdNat18,JaiWuAbdNat19} to be successful in using disentanglement learning methods for zero-label stratification. %\citet{JaiRexAbdNat18,JaiWuAbdNat19}.
%
We have some annotations of subgroup label $s$ in the training set $\Dcal_{tr} =\{(x_i, s_i, y_i)\}$, however, crucially, due to systematic bias, this set is missing certain subgroups.
%
We have all subgroups in the deployment set $\Dcal_{dep} =\{(x_i)\}$, 
%(also in the deployment set $\Dcal_{tr} =\{(x_i)\}$), 
though, the challenge is that the subgrouping information is unavailable or hidden at the deployment time.
%
In the following section, we show that we can still leverage the 
deployment set for learning the disentangled representations.

@@

\textbf{Disentanglement with a collection of perfect bags.} 
Our framework for learning the disentangled representations comprises four core modules: 1) \emph{encoder} functions $f_y$ and $f_s$ (which share weights) that embed $x$ into $z_y$ and $z_s$, respectively; 2) a \emph{decoder} function $g$
 that learns the approximate-inverse mapping of $f_y$ and $f_s$: $g: (z_y, z_s) \rightarrow \tilde{x}$; 3) \emph{predictor} functions $\ell_y$ and $\ell_s$ that predict $y$ and $s$ from $z_y$ and $z_s$ respectively, and 4) a \emph{discriminator} function $h$ that classifies a given bag of samples embedded in $z_y$ as deriving from the deployment set or the training set; this marks a significant departure from the typical GAN discriminator, which takes as input batches of data and yields a prediction for each sample independently of the other samples in the batch. 
 %
 Fig. \ref{fig:architecture} shows our framework. %, where the training signal comes from the perfect dataset.
 %
 Formally, given bags $\gB_{tr}$ from the training set, and \emph{balanced} (i.e. approximately perfect -- see section \ref{sec:implementation} for details on how this can be practically achieved) bags $\gB_\mathit{perf}$ from the deployment set, we first define, for notational convenience, the loss with respect to the encoder networks, $f_y$ and $f_s$ as
 \begin{align}
     &\,\mathcal{L}_{\text{enc}}(f_y, f_s, h) \nonumber\\
   =&\,\sum_{x \in \mathcal{B}_{tr} \bigcup \gB_\mathit{perf}} L_{\text{recon}} (x,g(f_y(x),f_s(x))) \nonumber\\
     &\,+ \!\!\sum_{x\in \Bcal_{tr}} \lambda_1 L_{\text{sup}} (y, \ell_y(f_y(x))) + \lambda_2 L_{\text{sup}} (s, \ell_s(f_s(x)))\nonumber\\
     &\,- \lambda_3 (
          \log h(\{f_y(x) | x \in \Bcal_\mathit{perf}\}) \nonumber\\
         &\quad\quad\,\,\, +  \log h(\{f_y(x) | x \in \mathcal{B}_{tr}\})
     ),
     \label{eq:disentangling}
 \end{align}

@@

Aside from being computed over a bag of samples, our adversarial loss differs from that the standard one in that both of its constituent terms are dependent on $f_y$ (the encoder is responsible for producing the ``real'' \emph{and} ``fake'' samples); we allow the gradient to flow through both of these terms, finding that adding a stop-gradient to $\log h(\{f_y(x) | x \in \Bcal_{perf}\})$ drastically reduced the convergence-rate and stability of the algorithm.

Eq.~(\ref{eq:disentangling_total}) is computed over batches of bags and the discriminator is trained to map a bag of data points from the training set and the deployment set to a binary label:
$1$ if the bag is judged to have been sampled from the deployment set, $0$ if from the training set.
% Its goal is to effectively estimate the probability that a bag of samples has been sampled from one distribution or the other.
Since the task is a set-classification one, we require that the function it defines respects the exchangeability of the bag dimension -- that is, the discriminator's predictions should take into account dependencies between samples in a bag but should be invariant to the order in which they appear, \ie\ we have $h(\{f_y(x_i)\}^\mathcal{B}_{b=i}) = h(\{f_y(x_i)\}^\mathcal{B}_{b=\pi (i)})$ for all permutations $\pi$.
To make the entirety of the function $h$ -- composed of sub-functions $h_1(h_2(h_3...)))$ -- have this property, requires only the innermost, sub-function, $\rho$ in the chain to have it.
While there are a number of choices when it comes to defining $\rho$, we choose a weighted average $\rho = \frac{1}{\mathcal{B}} \sum_i(\{\mathrm{attention}(f_y(x_i))\}^\mathcal{B}_{b=i})$, with weights computed according to a learned attention mechanism. The idea of using an attention mechanism for set-wise classification has been previously successfully explored by \citet{ilse2018attention} and  \citet{lee2019set};
we use the gated attention mechanism proposed by \citet{ilse2018attention} in the experiments, but also tried out the scaled dot-product attention per \citet{vaswani2017attention}, as the bag-wise pooling layer of our discriminator.
% For the latter, we had success defining K and V to be  $z_y$, and Q to be the mean of $z_y$ over $\mathcal{B}$.
% , weighting values (V) according to the similarity between the associated key (K) and query (Q) matrices, as measured by their dot-product. 
% Q, K, and V are not used directly but are first embedded into linear subspaces by matrix-multiplication with learned weight matrices of dimension $\mathbb{R}^{m\times d}$. 
% Q, K, and V are used after they have been embedded into linear subspaces by matrix-multiplication with learned weight matrices of dimension $\mathbb{R}^{m\times d}$. 
The result of $\rho$ is then processed by a series of fully-connected layers, following the DeepSets  \citep{zaheer2017deep} paradigm, which ultimately computes a single prediction for a given bag of samples.

@@

\subsection{Implementation}
\label{sec:implementation}
Our proposed framework, demonstrated in fig.\,\ref{fig:framework}, entails two steps: 1) sample perfect bags from an unlabeled deployment set, and 2) produce disentangled representations using perfect bags for adversarial distribution-matching.

@@

% The method of rank statistics \citep{YagStrRosLin11,DeaRuzSegShletal13,HanRebEhrVedetal20} avoids comparing the vectors $z_i$ and $z_j$ directly, and instead ranks the values in $z_i$ and in $z_j$ by their magnitudes, and compares the top-$U$ rankings (we found $U = 5$ to perform well in our experiments).
% %
% If the rankings obtained for two unlabeled data points $z_i$ and $z_j$ are the same, they are assigned to the same class, $s_{ij}=1$. 
% %
As a result of clustering, the data points in the deployment set $\Dcal_\mathit{dep}$ are labeled with cluster assignments 
$\Dcal_\mathit{dep}=\{(x_i, c_i)\}$, $c_i = C(z_i)$.
%
We balance $\Dcal_\mathit{dep}$ so that all clusters have equal size to form a perfect bag
% (see fig. \ref{fig:teaser})
, and use it as a supervision signal for the disentangling step.
%
%Note that our method of constructing the perfect dataset based on clustering does not require solving the linear assignment problem of cluster-source association. This is particularly suitable for exploring the setting where invisible demographics are formed of multiple sources.

@@

\section{Experiments}
We perform experiments using image and tabular datasets: Colored MNIST \citep{kim2019learning}, CelebA \cite{liu2015celeba} and Adult Income\footnote{{Results for Adult Income dataset and discussion can be found in the supplementary material.}} \citep{Dua:2017} that are publicly available. 
%arjovsky2019invariant, KehBarThoQua20
%
To validate the first step of creating the perfect bags, we compare the performance of our disentangling model when paired with each of four different balancing methods:
1) with clustering via rank statistics (\texttt{Ranking});
2) with clustering via k-means (\texttt{K-means}); 
3) without balancing, when the deployment set $\Dcal_{dep}$ is used as is (\texttt{No bal.});
4) with balancing done using the ground-truth class and subgroup labels (\texttt{Perfect}) that would in practice be unobservable; this provides insight into what can be achieved under ideal conditions and how sensitive the method is to imperfections in the bag-balancing.

>>>>

%\icmltitle{Learning with Perfect Bags:\\
%Addressing Hidden Stratification with Zero Labelled Data}
\textsc{Authors}:\\
Thomas Kehrenberg$^1$, Myles Bartlett$^1$, Oliver Thomas$^1$, and Novi Quadrianto$^1$ \\
\textsc{Affiliations}:\\
$^1$ Predictive Analytics Lab (PAL), University of Sussex, Brighton, UK\\
\textsc{Conference}:\;\;\textit{European Conference on Computer Vision} (ECCV), 2020 \\
% \textsc{DOI}:\;\;10.3389/frai.2020.00033
\textsc{Note}:\;\;The appendix has been included as section~\ref{sec:sec:zsf-appendix}.

@@

Specifically, our paper provides the following contributions:
\begin{enumerate}
    \item An example of systematic bias leading to one or more  subgroups having \emph{zero labelled data}.
    \item Applying clustering methods to the task of transforming an \emph{unlabelled dataset} into perfect bags.
    \item Theoretical and experimental justification that the disentangling model with \emph{the perfect bag as an inductive bias} provides a well-disentangled representation, where one component captures the subgrouping factors and another component is invariant to them.
    \item A new parametric approach to disentangling that combines elements from adversarial learning and set-classification to guide an encoder network towards the goal of producing encodings invariant to the source distribution and thereby the subgroup factors in which source distributions differ.
\end{enumerate}

@@

%\begin{wrapfigure}{!t}{0.6\textwidth}
\begin{figure}[ht]
\centering
    %\includegraphics[width=0.9\textwidth]{figures/SSL-framework}
    % \includegraphics[width=\textwidth]{figures/SSL-framework-withPred.pdf}
    \includegraphics[width=\textwidth]{figures/zsf_diagram.pdf}
    \caption{%
    The main components involved in our proposed disentangling method, $f_y$ (debiaser) and $h$ (discriminator). The debiaser is trained to produce encodings, $z_y$ of the data that are invariant to the source dataset and thereby the subgroups identifying it. In order to determine whether a bag of encodings originates from the training set or the deployment set, the discriminator performs an attention-weighted aggregation over the bag dimension to model interdependencies between the samples. In the case of Coloured MNIST where {\color{purple}purple} fours constitute the missing subgroup, the discriminator can identify an encoding of a bag from the training set by the absence of such samples so long as colour information is detectable in $z_y$, serving as an error signal for the debiaser.
    }%
    \label{fig:architecture}
\end{figure}%
% \end{figure}
%\end{wrapfigure}
% \hfill
% \begin{figure}
\begin{figure}[ht]
    \centering
    % if you want to make changes to the diagram, it is located here:
    % https://drive.google.com/file/d/1M37m4rVj1EGrFJb9QzK32bs8swepiaZ1/view?usp=sharing
    \includegraphics[width=\textwidth]{figures/fdm.pdf}
    \caption{%
    Illustration of distribution matching.
    In this example, the training set is lacking {\color{purple}purple} 4's.
    By enforcing the subspace $z_y$ to have the same distribution for both the training and deployment set, the model is encouraged to learn a representation that is invariant to colour (or $s$ in general.)
    For this to work, it is crucial that the bags be approximately balanced (perfect bags).
    }%
    \label{fig:matching-diagram}
% \end{subfigure}
% \caption{%
% Overview of the disentangling framework with a perfect (balanced) bag as an inductive bias.
% }%
% \label{fig:framework}
\end{figure}

@@

\textbf{Zero-label stratification and algorithmic bias.}
Let $S$ denote a set of discrete-valued subgroup labels of the associated domains $\gS$.
%
% $S$ can take the values taken by a single subclass label, or, $S = S_1 \times S_2 \times \ldots \times S_p$ with $S_1, \ldots, S_p$ be discrete-valued subclass labels more generally.
%
$X$, with the associated domain $\gX$, represents other attributes of the data. % that may or may not be influenced by subgroup labels $S$.
%
Let $\gY$ denote the space of class labels for a classification task; $\gY = \{0,1\}$ for binary classification or $\gY = \{1,2,\ldots,C_{\text{cls}}\}$ for multi-class classification.
%
For ease of exposition, we assume that we have multiple sources $\Omega$ of samples, one for each combination of class-label $y$ and subgroup-label $s$.
That is, we have:
\begin{align}
\Omega_{y=y',s=s'},\quad\quad\forall y'\in\mathcal{Y},\forall s'\in\mathcal{S},
\end{align}
where, for example, the source $\Omega_{y=0,s=0}$ supplies all data points with class label $y=0$ and subgroup label $s=0$. 
%
As in a standard supervised learning task, we have access to a labelled training set $\gD_{tr} =\{(x_i, s_i, y_i)\}$, that is used to learn a model $M:\gX \rightarrow \gY$. 
$\gD_{tr}$ is composed of several sources, but lacks samples from some of the sources:
\begin{align}
\exists y'\in \gY,\exists s'\in \gS: \gD_{tr}\cap \Omega_{y=y',s=s'} = \varnothing.
\end{align}
For example, we might be missing samples from two sources: $\Omega_{y=0,s=0}$ and $\Omega_{y=1,s=0}$. 
%
In binary classification, this corresponds to no labelled data for the subgroup label $s=0$, a setting we refer to as \emph{missing subgroup} (MS).
%
Other times, we may observe a one-sided (negative) outcome for the subgroup label $s=0$
(\ie, we have $\gD_\mathit{tr} \cap\Omega_{y=1,s=0} = \varnothing$), giving rise to a setting we refer to as \emph{subgroup bias} (SB).

@@

%Semi-supervised learning \cite{ChaSchZie06} can alleviate the issue of unfairness to the \emph{invisibles} by mixing labeled with unlabeled data, which is usually much cheaper to obtain. 
%
We propose to alleviate the issue of bias against missing subgroups by mixing labelled data with unlabelled data that is usually much cheaper to obtain \cite{ChaSchZie06}. 
%
In this paper, we refer to this set of \emph{unlabelled} data as the
deployment set\footnote{In our experiments, we report accuracy and bias metrics on another independent test set instead of on the unlabelled data that is available at training time.} $\gD_{dep} =\{(x_i)\}$.
%_{i=1}^{N^c}
%
This 
%context 
deployment set has overlap with all sources:
\begin{align}
  \gD_{dep} \cap \Omega_{y=y',s=s'} \neq \varnothing\quad\quad\forall y'\in\gY,\forall s'\in\gS~.
\end{align}
%The deployment set is much like the deployment set: 
Importantly, the deployment set has no information about class labels $y$ or the subgroup labels $s$.

@@

\textbf{Disentangled representation.}
Disentanglement-learning aims to find a factorised representation of a data point $x$ through mapping functions $f_i$ such that $f_i(x)=z_i$ where $z_1,z_2,\ldots,z_p$ are $p$ distinct (independent) factors of variations, which together form $x$.
%
We can formalise this intuitive definition using group and representation theories \cite{HigAmoPfaRacetal18}, or using structural causal models \cite{SutMilSchBau19}.
%
Specifically for this paper, we would like to split the data representation into two factors as $f_y(x)=z_y$ and $f_s(x)=z_s$ where $z_y$ contains factors that are relevant for $y$-prediction and $z_s$ contains factors related to the subgroup label $s$.
%
Since $s$ is correlated with the class label $y$, we need annotations of the undesired nuisance variable $s$ \cite{JaiRexAbdNat18,JaiWuAbdNat19} to be successful in using disentanglement learning methods for zero-label stratification. %\citet{JaiRexAbdNat18,JaiWuAbdNat19}.
%
We have some annotations of subgroup label $s$ in the training set $\gD_{tr} =\{(x_i, s_i, y_i)\}$, however, crucially, due to systematic bias, this set is missing certain subgroups.
%
We have all subgroups in the deployment set $\gD_{dep} =\{(x_i)\}$, 
%(also in the deployment set $\Dcal_{tr} =\{(x_i)\}$), 
though, the challenge is that the subgrouping information is unavailable or hidden at the deployment time.
%
In the following section, we show that we can still leverage the 
deployment set for learning the disentangled representations.

@@

\textbf{Disentanglement with a collection of perfect bags.} 
Our framework for learning the disentangled representations comprises four core modules: 1) \emph{encoder} functions $f_y$ and $f_s$ (which share weights) that embed $x$ into $z_y$ and $z_s$, respectively; 2) a \emph{decoder} function $g$
 that learns the approximate-inverse mapping of $f_y$ and $f_s$: $g: (z_y, z_s) \rightarrow \tilde{x}$; 3) \emph{predictor} functions $\ell_y$ and $\ell_s$ that predict $y$ and $s$ from $z_y$ and $z_s$ respectively, and 4) a \emph{discriminator} function $h$ that classifies a given bag of samples embedded in $z_y$ as deriving from the deployment set or the training set; this marks a significant departure from the typical GAN discriminator, which takes as input batches of data and yields a prediction for each sample independently of the other samples in the batch. 
 %
 Fig. \ref{fig:architecture} shows our framework. %, where the training signal comes from the perfect dataset.
 %
 Formally, given bags $\gB_{tr}$ from the training set, and \emph{balanced} (i.e. approximately perfect -- see section \ref{sec:implementation} for details on how this can be practically achieved) bags $\gB_\mathit{perf}$ from the deployment set, we first define, for notational convenience, the loss with respect to the encoder networks, $f_y$ and $f_s$ as
 \begin{align}
     &\,\mathcal{L}_{\text{enc}}(f_y, f_s, h) \nonumber\\
   =&\,\sum_{x \in \mathcal{B}_{tr} \bigcup \gB_\mathit{perf}} L_{\text{recon}} (x,g(f_y(x),f_s(x))) \nonumber\\
     &\,+ \!\!\sum_{x\in \gB_{tr}} \lambda_1 L_{\text{sup}} (y, \ell_y(f_y(x))) + \lambda_2 L_{\text{sup}} (s, \ell_s(f_s(x)))\nonumber\\
     &\,- \lambda_3 (
          \log h(\{f_y(x) | x \in \gB_\mathit{perf}\}) \nonumber\\
         &\quad\quad\,\,\, +  \log h(\{f_y(x) | x \in \mathcal{B}_{tr}\})
     ),
     \label{eq:disentangling}
 \end{align}

@@

Aside from being computed over a bag of samples, our adversarial loss differs from that the standard one in that both of its constituent terms are dependent on $f_y$ (the encoder is responsible for producing the ``real'' \emph{and} ``fake'' samples); we allow the gradient to flow through both of these terms, finding that adding a stop-gradient to $\log h(\{f_y(x) | x \in \gB_\mathit{perf}\})$ drastically reduced the convergence-rate and stability of the algorithm.

Eq.~(\ref{eq:disentangling_total}) is computed over batches of bags and the discriminator is trained to map a bag of data points from the training set and the deployment set to a binary label:
$1$ if the bag is judged to have been sampled from the deployment set, $0$ if from the training set.
% Its goal is to effectively estimate the probability that a bag of samples has been sampled from one distribution or the other.
Since the task is a set-classification one, we require that the function it defines respects the exchangeability of the bag dimension -- that is, the discriminator's predictions should take into account dependencies between samples in a bag but should be invariant to the order in which they appear,
\ie\ we have
\(h(\{f_y(x_i)\}^\gB_{b=i}) = h(\{f_y(x_i)\}^\gB_{b=\pi (i)})\)
for all permutations $\pi$.
To make the entirety of the function $h$ -- composed of sub-functions $h_1(h_2(h_3...)))$ -- have this property, requires only the innermost, sub-function, $\rho$ in the chain to have it.
While there are a number of choices when it comes to defining $\rho$, we choose a weighted average $\rho = \frac{1}{\gB} \sum_i(\{\mathrm{attention}(f_y(x_i))\}^\gB_{b=i})$, with weights computed according to a learned attention mechanism. The idea of using an attention mechanism for set-wise classification has been previously successfully explored by \citet{ilse2018attention} and  \citet{lee2019set};
we use the gated attention mechanism proposed by \citet{ilse2018attention} in the experiments, but also tried out the scaled dot-product attention per \citet{vaswani2017attention}, as the bag-wise pooling layer of our discriminator.
% For the latter, we had success defining K and V to be  $z_y$, and Q to be the mean of $z_y$ over $\mathcal{B}$.
% , weighting values (V) according to the similarity between the associated key (K) and query (Q) matrices, as measured by their dot-product. 
% Q, K, and V are not used directly but are first embedded into linear subspaces by matrix-multiplication with learned weight matrices of dimension $\mathbb{R}^{m\times d}$. 
% Q, K, and V are used after they have been embedded into linear subspaces by matrix-multiplication with learned weight matrices of dimension $\mathbb{R}^{m\times d}$. 
The result of $\rho$ is then processed by a series of fully-connected layers, following the DeepSets  \citep{zaheer2017deep} paradigm, which ultimately computes a single prediction for a given bag of samples.

@@

\subsection{Implementation}
\label{sec:implementation}
Our proposed framework, demonstrated in fig.\,\ref{fig:architecture}, entails two steps: 1) sample perfect bags from an unlabeled deployment set, and 2) produce disentangled representations using perfect bags for adversarial distribution-matching.

@@

% The method of rank statistics \citep{YagStrRosLin11,DeaRuzSegShletal13,HanRebEhrVedetal20} avoids comparing the vectors $z_i$ and $z_j$ directly, and instead ranks the values in $z_i$ and in $z_j$ by their magnitudes, and compares the top-$U$ rankings (we found $U = 5$ to perform well in our experiments).
% %
% If the rankings obtained for two unlabeled data points $z_i$ and $z_j$ are the same, they are assigned to the same class, $s_{ij}=1$. 
% %
As a result of clustering, the data points in the deployment set $\gD_\mathit{dep}$ are labeled with cluster assignments 
$\gD_\mathit{dep}=\{(x_i, c_i)\}$, $c_i = C(z_i)$.
%
We balance $\gD_\mathit{dep}$ so that all clusters have equal size to form a perfect bag
% (see fig. \ref{fig:teaser})
, and use it as a supervision signal for the disentangling step.
%
%Note that our method of constructing the perfect dataset based on clustering does not require solving the linear assignment problem of cluster-source association. This is particularly suitable for exploring the setting where invisible demographics are formed of multiple sources.

@@

\section{Experiments}
We perform experiments using image and tabular datasets: Colored MNIST \citep{kim2019learning}, CelebA \cite{liu2015celeba} and Adult Income\footnote{{Results for Adult Income dataset and discussion can be found in the supplementary material.}} \citep{Dua:2017} that are publicly available. 
%arjovsky2019invariant, KehBarThoQua20
%
To validate the first step of creating the perfect bags, we compare the performance of our disentangling model when paired with each of four different balancing methods:
1) with clustering via rank statistics (\texttt{Ranking});
2) with clustering via k-means (\texttt{K-means}); 
3) without balancing, when the deployment set $\gD_{dep}$ is used as is (\texttt{No bal.});
4) with balancing done using the ground-truth class and subgroup labels (\texttt{Perfect}) that would in practice be unobservable; this provides insight into what can be achieved under ideal conditions and how sensitive the method is to imperfections in the bag-balancing.
